\vspace{1.0cm} \LARGE \bf Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2014-02-09 fluB.tex
Updating most figures, adding new supp ones.
Updating all figures with (hopefully) their latest versions. Changes are
either the M1-MP/NS1-NS issue or colour scheme updates. I didn't update
some, since I'm re-running some trees due to labeling issues.
Also adding a lot of supplementary figures relating to exact-approximate
SPR distances. Basically showing that approximate SPR distances are
reasonable overestimates of exact SPR distances.

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_RErate_trees.png}
\caption{\textbf{Reassortment rate (approximate number of SPR moves per total time in both trees) between all pairs of trees of segments.}}
\label{}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_RErate_replicates.png}
\caption{\textbf{Reassortment rate (approximate number of SPR moves per total time in the tree) between replicate trees of each segment.}}
\label{}
\end{figure}

@@

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB1-PB2_hist.png}
\caption{\textbf{Distribution of differences between exact and approximate PB1-PB2 SPR distances after normalization.}}
\label{SPR_PB1-PB2_difference}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB1-PB2_hist2.png}
\caption{\textbf{Distribution of ratios between exact and approximate PB1-PB2 SPR distances after normalization.}}
\label{SPR_PB1-PB2_ratio}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB1-HA_hist.png}
\caption{\textbf{Distribution of differences between exact and approximate PB1-HA SPR distances after normalization.}}
\label{SPR_PB1-HA_difference}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB1-HA_hist2.png}
\caption{\textbf{Distribution of ratios between exact and approximate PB1-HA SPR distances after normalization.}}
\label{SPR_PB1-HA_ratio}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB2-HA_hist.png}
\caption{\textbf{Distribution of differences between exact and approximate PB2-HA SPR distances after normalization.}}
\label{SPR_PB2-HA_difference}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB2-HA_hist2.png}
\caption{\textbf{Distribution of ratios between exact and approximate PB2-HA SPR distances after normalization.}}
\label{SPR_PB2-HA_ratio}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.5\textwidth]  {supp_figures/InfB_supp_PB1-PB2_corr.png}
\caption{\textbf{Correlation between exact and approximate PB1-PB2 SPR distances after normalization.}}
\label{SPR_PB1-PB2_correlation}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.5\textwidth]  {supp_figures/InfB_supp_PB1-HA_corr.png}
\caption{\textbf{Correlation between exact and approximate PB1-HA SPR distances after normalization.}}
\label{SPR_PB1-HA_correlation}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.5\textwidth]  {supp_figures/InfB_supp_PB2-HA_corr.png}
\caption{\textbf{Correlation between exact and approximate PB2-HA SPR distances after normalization.}}
\label{SPR_PB2-HA_correlation}
\end{figure}

>>>>

@@

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_NormPB1-PB2_hist.png}
\caption{\textbf{Distribution of differences between exact and approximate PB1-PB2 SPR distances after normalization.}}
\label{NormSPR_PB1-PB2_difference}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_NormPB1-PB2_hist2.png}
\caption{\textbf{Distribution of ratios between exact and approximate PB1-PB2 SPR distances after normalization.}}
\label{NormSPR_PB1-PB2_ratio}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_NormPB1-HA_hist.png}
\caption{\textbf{Distribution of differences between exact and approximate PB1-HA SPR distances after normalization.}}
\label{NormSPR_PB1-HA_difference}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_NormPB1-HA_hist2.png}
\caption{\textbf{Distribution of ratios between exact and approximate PB1-HA SPR distances after normalization.}}
\label{NormSPR_PB1-HA_ratio}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_NormPB2-HA_hist.png}
\caption{\textbf{Distribution of differences between exact and approximate PB2-HA SPR distances after normalization.}}
\label{NormSPR_PB2-HA_difference}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB2-HA_hist2.png}
\caption{\textbf{Distribution of ratios between exact and approximate PB2-HA SPR distances after normalization.}}
\label{NormSPR_PB2-HA_ratio}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.5\textwidth]  {supp_figures/InfB_supp_NormPB1-PB2_corr.png}
\caption{\textbf{Correlation between exact and approximate PB1-PB2 SPR distances after normalization.}}
\label{NormSPR_PB1-PB2_correlation}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.5\textwidth]  {supp_figures/InfB_supp_NormPB1-HA_corr.png}
\caption{\textbf{Correlation between exact and approximate PB1-HA SPR distances after normalization.}}
\label{NormSPR_PB1-HA_correlation}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.5\textwidth]  {supp_figures/InfB_supp_NormPB2-HA_corr.png}
\caption{\textbf{Correlation between exact and approximate PB2-HA SPR distances after normalization.}}
\label{NormSPR_PB2-HA_correlation}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB1-PB2_hist.png}
\caption{\textbf{Distribution of differences between exact and approximate PB1-PB2 SPR distances.}}
\label{SPR_PB1-PB2_difference}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB1-PB2_hist2.png}
\caption{\textbf{Distribution of ratios between exact and approximate PB1-PB2 SPR distances.}}
\label{SPR_PB1-PB2_ratio}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB1-HA_hist.png}
\caption{\textbf{Distribution of differences between exact and approximate PB1-HA SPR distances.}}
\label{SPR_PB1-HA_difference}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB1-HA_hist2.png}
\caption{\textbf{Distribution of ratios between exact and approximate PB1-HA SPR distances.}}
\label{SPR_PB1-HA_ratio}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB2-HA_hist.png}
\caption{\textbf{Distribution of differences between exact and approximate PB2-HA SPR distances.}}
\label{SPR_PB2-HA_difference}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_PB2-HA_hist2.png}
\caption{\textbf{Distribution of ratios between exact and approximate PB2-HA SPR distances after.}}
\label{SPR_PB2-HA_ratio}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.4\textwidth]  {supp_figures/InfB_supp_PB1-PB2_corr.png}
\caption{\textbf{Correlation between exact and approximate PB1-PB2 SPR distances after.}}
\label{SPR_PB1-PB2_correlation}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.4\textwidth]  {supp_figures/InfB_supp_PB1-HA_corr.png}
\caption{\textbf{Correlation between exact and approximate PB1-HA SPR distances after.}}
\label{SPR_PB1-HA_correlation}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.4\textwidth]  {supp_figures/InfB_supp_PB2-HA_corr.png}
\caption{\textbf{Correlation between exact and approximate PB2-HA SPR distances.}}
\label{SPR_PB2-HA_correlation}
\end{figure}
